### 2021-03-09 README.Rmd

1. Calculates accuracy, lower and upper bounds, the guessing rate and p-value of the accuracy vs. the guessing rate. 
2. Calculates by class the following statistics:
  - Sensitivity = A/(A+C)
  - Specificity = D/(B+D)
  - Prevalence = (A+C)/(A+B+C+D)
  - Positive Predictive Value = (sensitivity * prevalence)/((sensitivity*prevalence) + ((1-specificity)*(1-prevalence)))
  - Negative Predictive Value = (specificity * (1-prevalence))/(((1-sensitivity)*prevalence) + ((specificity)*(1-prevalence)))
  - Detection Rate = A/(A+B+C+D)
  - Detection Prevalence = (A+B)/(A+B+C+D)
  - Balanced Accuracy = (sensitivity+specificity)/2
  - Precision = A/(A+B)
  - Recall = A/(A+C)
  - F1 = harmonic mean of precision and recall
  - False Discovery Rate = 1 - Positive Predictive Value
  - False Omission Rate = 1 - Negative Predictive Value
  - False Positive Rate = 1 - Specificity
  - False Negative Rate = 1 - Sensitivity
3. The contingency table object itself.

>>>>

1. Calculates accuracy, lower and upper bounds, the guessing rate and p-value of the accuracy vs. the guessing rate. 
2. Calculates by class the following statistics:
    - Sensitivity = A/(A+C)
    - Specificity = D/(B+D)
    - Prevalence = (A+C)/(A+B+C+D)
    - PPV = (sensitivity * prevalence)/((sensitivity * prevalence) + ((1-specificity) * (1-prevalence)))
    - NPV = (specificity * (1-prevalence))/(((1-sensitivity) * prevalence) + ((specificity) * (1-prevalence)))
    - Detection Rate = A/(A+B+C+D)
    - Detection Prevalence = (A+B)/(A+B+C+D)
    - Balanced Accuracy = (sensitivity+specificity)/2
    - Precision = A/(A+B)
    - Recall = A/(A+C)
    - F1 = harmonic mean of precision and recall
    - False Discovery Rate = 1 - PPV
    - False Omission Rate = 1 - NPV
    - False Positive Rate = 1 - Specificity
    - False Negative Rate = 1 - Sensitivity
3. The contingency table object itself.
